Positivity-Preserving Adaptive Runge--Kutta Methods

### 2020-03-31 nusslein_vsrp/latex/overview.tex
additional software references

The implementation of the algorithms described above and code to
reproduce the numerical examples reported here can be found in
\cite{repository}. \todo{TODO: New reopsitory with DOI} %TODO
We have used CVXPY to solve the LPs \cite{cvxpy, cvxpy_rewriting}.
\todo{TODO: Which solver of CVXPY?} %TODO

>>>>

The implementation of the algorithms described above and code to
reproduce the numerical examples reported here can be found in
\cite{repository}. \todo{TODO: New reopsitory with DOI} %TODO
The methods are implemented in Python using NumPy/SciPy
\cite{virtanen2019scipy}, NodePy \cite{nodepy08}, and
Matplotlib \cite{hunter2007matplotlib} for the visualizations.
We have used CVXPY to solve the LPs \cite{cvxpy, cvxpy_rewriting}.
\todo{TODO: Which solver of CVXPY?} %TODO
